Reactive SINDy: Discovering governing reactions from concentration data

### 2018-11-28 docs/manuscript_jcp.tex

%% LyX 2.3.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,osajnl,jcp,preprint,groupedaddress,noshowpacs,showkeys,longbibliography,noeprint,nofootinbib,bibtex,ruled,vlined,english,natural,table,usenames,dvipsnames,a4paper]{revtex4-1}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\setcounter{secnumdepth}{3}
\usepackage{color}
\usepackage{babel}
\usepackage{array}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage[unicode=true,
bookmarks=false,
breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=true]
{hyperref}
%\hypersetup{%
%	linkcolor=BrickRed,urlcolor=blue!50!black,citecolor=blue!50!black}

@@

@@

The goal is to find coefficients $\Xi=\begin{pmatrix}\xi_{1} & \xi_{2} & \cdots & \xi_{R}\end{pmatrix}^{\top}$,
so that 
\begin{align}
\dot{\textbf{X}}=\Theta(\textbf{X})\Xi=\sum_{r=1}^{R}\theta_{r}(\textbf{X})\xi_{r}.
\end{align}
In particular, the system is linear in the coefficients $\Xi$, which
makes regression tools such as elastic net regularization~\cite{Zou2005}
applicable. To this end, one can consider the regularized minimization
problem (reactive SINDy): 
\begin{align}
\hat{\Xi}=\underset{\Xi}{\arg\min}\left(\frac{1}{2T}\left\Vert \dot{\textbf{X}}-\Theta(\textbf{X})\Xi\right\Vert _{F}^{2}+\alpha\lambda\|\Xi\|_{1}+\alpha(1-\lambda)\|\Xi\|_{2}^{2}\right)\quad\text{subject to }\Xi\geq0.\label{method:minimizationproblem}
\end{align}
Here, $\|\cdot\|_{F}$ denotes the Frobenius norm, $\lambda\in[0,1]$
is a hyperparameter that interpolates linearly between LASSO~\cite{Tibshirani1996,Hastie2009}
and Ridge~\cite{Hoerl1} methods, and $\alpha\geq0$ is a hyperparameter
that, depending on $\lambda$, can induce sparsity and give preference
to smaller solutions in the $L_{1}$ or $L_{2}$ sense. For $\alpha=0$
the minimization problem reduces to standard least-squares (LSQ) with
the constraint $\Xi\geq0$. Reactive SINDy (\ref{method:minimizationproblem})
is therefore a generalization of the SINDy method to to the vector-valued
ansatz functions.

@@

We demonstrate the method by estimating the reactions of a gene-regulatory
network from time series of concentrations of the involved molecules.
Let $S:=\{A,B,C\}$ be a set of three species of proteins which are
being translated each from their respective $\mathrm{mRNA}$ molecule.
Each $\mathrm{mRNA}$ in turn has a corresponding $\mathrm{DNA}$
which it is transcribed from. The proteins and $\mathrm{mRNA}$ molecules
decay over time whereas the $\mathrm{DNA}$ concentration remains
constant. The network contains reactions of the following form~\cite{Thattai2001a}
\begin{align*}
\mathrm{DNA}_{i} & \rightharpoonup\mathrm{DNA}_{i}+\mathrm{mRNA}_{i} &  & \text{(transcription)},\\
\mathrm{mRNA}_{i} & \rightharpoonup\mathrm{mRNA}_{i}+i &  & \text{(translation)},\\
\mathrm{mRNA}_{i} & \rightharpoonup\emptyset &  & \text{(decay of mRNA)},\\
i & \rightharpoonup\emptyset &  & \text{(decay of protein)},\\
i+\mathrm{mRNA}_{j} & \rightharpoonup i &  & \text{(regulation of protein }j\in S\text{),}
\end{align*}
for each of the species $i\in S$. These reactions model a regulation
of species $j$ by virtue of the fact that the transcription product
inhibits the transcription processes. In our example proteins of type
$\mathrm{A}$ regulate the $\mathrm{mRNA}_{\mathrm{B}}$ molecules,
proteins of type $\mathrm{B}$ regulate the $\mathrm{mRNA}_{\mathrm{C}}$
molecules and proteins of type $\mathrm{C}$ regulate the $\mathrm{mRNA}_{\mathrm{A}}$
molecules (Fig.~\ref{fig:network}). Using this reaction model, time
series of concentrations are generated using the rates given in Tab~\ref{tab:reaction-library}
under the initial condition described in Tab~\ref{tab:Initial-conditions}a,
which were chosen so that all the reactions in the reaction model
significantly contribute to the temporal evolution of the system's
concentrations. The generation samples the integrated equations equidistantly
with a discrete time step of $\tau=3\cdot10^{-3}$ yielding $667$
frames which amounts to a cumulative time of roughly $T=2$.

\begin{figure}
\centering \includegraphics[width=\singlecolumnwidth]{figures_tex/scheme}
\caption{\label{fig:network}The regulation network example described in Sec.~\ref{sec:results}.
Each circle depicts a species, each arrow corresponds to one reaction.
Blue arrows denote transcription from $\mathrm{DNA}$ to $\mathrm{mRNA}$,
green arrows denote translation from $\mathrm{mRNA}$ to protein,
and red arrows denote the regulatory network.}
\end{figure}
\begin{table}
\centering%
\begin{tabular}{cccccccccc}
 & $\mathrm{DNA}_{\mathrm{A}}$ & $\mathrm{mRNA}_{\mathrm{A}}$ & $\mathrm{A}$ & $\mathrm{DNA}_{\mathrm{B}}$ & $\mathrm{mRNA}_{\mathrm{B}}$ & $\mathrm{B}$ & $\mathrm{DNA}_{\mathrm{C}}$ & $\mathrm{mRNA}_{\mathrm{C}}$ & $\mathrm{C}$\tabularnewline
\midrule
\textbf{(a)} & $1$ & $2$ & $0$ & $1$ & $0$ & $3$ & $1$ & $0$ & $0$\tabularnewline
\textbf{(b)} & $1$ & $1.5$ & $0$ & $1$ & $0$ & $2$ & $1$ & $0$ & $1$\tabularnewline
\end{tabular}\caption{\label{tab:Initial-conditions}Initial conditions used to generate
concentration time series. Reaction rates can be found in Tab.~\ref{tab:reaction-library}.}
\end{table}
The proposed estimation method is applied to analyze these time series
of concentrations in order to recover the underlying reaction network
from data. To this end we use the library of ansatz functions given
in Tab.~\ref{tab:reaction-library}, which contains a large number
of possible reactions, only few of which are actually part of the
model.

@@

We first set the hyperparameter $\alpha=0$ in the minimization problem
(\ref{method:minimizationproblem}), which results in constrained
least-squares regression without any of the regularization terms.
In this case we estimate a reaction network that can reproduce the
observations almost exactly (Fig.~\ref{fig:case-1-lsq}). However,
the result is mechanistically wrong as the sparsity pattern does not
match the reaction network used to generate the data. On the one hand
many spurious reactions are estimated that were not in the true reaction
scheme and would lead to wrong conclusions about the mechanism, such
as $\mathrm{A}+\mathrm{A}\rightharpoonup\mathrm{A}$ and $\mathrm{A}+\mathrm{C}\rightharpoonup\mathrm{C}$.
More dramatically, the reaction responsible for the decay of $\mathrm{A}$
particles is completely ignored (Fig.~\ref{fig:case-1-sparsity-pattern}).

\begin{figure}
\centering\includegraphics[width=\singlecolumnwidth]{figures_tex/trajectories_lsq}\caption{\label{fig:case-1-lsq}Concentration time series generated from integrating
the reaction network shown in Fig.~\ref{fig:network}a. The initial
condition prescribes positive concentration values only for $\mathrm{B}$
protein and $\mathrm{mRNA}_{\mathrm{A}}$ species (Tab.~\ref{tab:Initial-conditions}a).
This initial condition is used in the subsequent sections for further
analysis. Gray dots depict concentration time series yielded from
the LSQ rates estimated in Sec~\ref{sec:case-1}.}
\end{figure}
\begin{figure}
\centering \includegraphics[width=0.82\doublecolumnwidth]{figures_tex/sparsity_pattern}
\caption{\label{fig:case-1-sparsity-pattern}Estimated reaction rates in the
system described in Sec.~\ref{sec:case-1}. The y and x axes contain
reaction educts and products, respectively. A circle at position $(i,j)$
represents a reaction $i\rightharpoonup j$ whose rate has a linear
relation with the area of the circle. The black outlines denote the
reactions with which the system was generated and contain the respective
rate value. Red crosses denote reactions that were used as additional
ansatz reactions. Blue circles are estimated by LSQ and orange circles
depict rates which were obtained by solving the minimization problem
(\ref{method:minimizationproblem}). The latter rates are subject
to a cutoff $\kappa=0.22$ corresponding to the green circle's area
under which a sparse solution with the correct processes can be recovered.
If a certain rate was estimated in both cases, two wedges instead
of one circle are displayed.}
\end{figure}
Next, we sought sparse solutions by using $\alpha>0$ and additionally
eliminating reactions with rate constants smaller than a cutoff value
$\kappa$. For a suitable choice of hyperparameters $\alpha\approx1.91\cdot10^{-7}$,
$\lambda=1$, and $\kappa=0.22$, a sparse solution is obtained that
finds the correct reaction scheme and also recovers the decay reaction
(Fig.~\ref{fig:case-1-sparsity-pattern}).

@@

\begin{figure}
\centering \includegraphics[width=\singlecolumnwidth]{figures_tex/case2}
\caption{\label{fig:case2-convergence}Convergence of the estimation error
when estimating the system described in Sec.~\ref{sec:case-1} with
varying levels of noise by application of reactive SINDy (\ref{method:minimizationproblem})
with and without regularization in blue and orange, respectively.
The procedure was independently repeated $10$ times with different
realizations giving rise to the mean and standard deviation depicted
by solid lines and shaded areas, respectively. \textbf{(a)}: The number
of detected spurious reactions up to the cutoff value introduced in
Sec.~\ref{sec:case-1} over different levels of noise. \textbf{(b)}:
The estimation error given by the mean absolute error between the
generating reaction rates $\xi$ and the estimated reaction rates
$\hat{\xi}$ over different levels of noise.}
\end{figure}
The hyperparameters $(\alpha,\lambda)$ are obtained by shuffling
the data and performing a $10$-fold cross validation.

@@

\begin{figure}
\centering \includegraphics[width=\singlecolumnwidth]{figures_tex/case3}
\caption{\label{fig:case3-convergence}Convergence of estimation error of reaction
schemes from noisy gene-regulation data starting from two different
initial conditions under decreasing levels of noise. The minimization
problem (\ref{method:minimizationproblem}) was solved for $\alpha=0$
(LSQ) and with regularization. This was repeated $10$ times on different
sets of observation data generated by Gillespie SSA, giving rise to
mean and standard deviation (solid lines and shaded areas, respectively).
\textbf{(a)}: Concentration time series corresponding to the initial
conditions, generated by integrating the reaction-rate equations.
The first initial condition is identical to the one used in Sec.~\ref{sec:case-1}
and Sec.~\ref{sec:case-2}. The second initial condition (Tab.~\ref{tab:Initial-conditions}b)
prescribes positive initial concentrations for $\mathrm{mRNA}_{\mathrm{A}}$,
$\mathrm{B}$, and $\mathrm{C}$ species. The gray graphs are sample
realizations of integration using the Gillespie SSA. \textbf{(b)},\textbf{(c)}:
Analogously to Fig.~\ref{fig:case2-convergence} with the difference
that 20-fold cross validation was used for hyperparameter estimation.}
\end{figure}
The hyperparameters $(\alpha,\lambda)$ are obtained by shuffling
the data and performing a $20$-fold cross validation.

@@

\centering\includegraphics[width=\singlecolumnwidth]{figures_tex/case1_cutoff}\caption{\label{fig:reaction-rates-sorted}Reaction rates sorted by their magnitude
to determine the cutoff $\kappa=0.22$ of Sec.~\ref{sec:case-1}.
The rates were estimated using the regularized minimization problem.}

@@

@@

\resizebox{.8\textwidth}{!}{%

@@

\end{tabular}}\caption{\label{tab:reaction-library}Full set of ansatz reactions $\Theta$

@@

\linespread{1.5}

>>>>

%% LyX 2.3.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,osajnl,jcp,reprint,groupedaddress,noshowpacs,showkeys,longbibliography,noeprint,nofootinbib,bibtex,ruled,vlined,english,natural,table,usenames,dvipsnames,a4paper]{revtex4-1}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\setcounter{secnumdepth}{3}
\usepackage{color}
\usepackage{babel}
\usepackage{array}
\usepackage{booktabs}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{microtype}
\usepackage[unicode=true,
bookmarks=false,
breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=true]
{hyperref}
%\hypersetup{%
%	linkcolor=BrickRed,urlcolor=blue!50!black,citecolor=blue!50!black}

@@

\newif\ifthisispreprint
% \thisispreprinttrue
\thisispreprintfalse

@@

The goal is to find coefficients $\Xi=\begin{pmatrix}\xi_{1} & \xi_{2} & \cdots & \xi_{R}\end{pmatrix}^{\top}$,
so that 
\begin{align}
\dot{\textbf{X}}=\Theta(\textbf{X})\Xi=\sum_{r=1}^{R}\theta_{r}(\textbf{X})\xi_{r}.
\end{align}
In particular, the system is linear in the coefficients $\Xi$, which
makes regression tools such as elastic net regularization~\cite{Zou2005}
applicable. To this end, one can consider the regularized minimization
problem (reactive SINDy): 
\begin{align}
\hat{\Xi}&=\underset{\Xi}{\arg\min}\Bigg(\frac{1}{2T}\left\Vert \dot{\textbf{X}}-\Theta(\textbf{X})\Xi\right\Vert _{F}^{2} \label{method:minimizationproblem} \\
&\quad+\alpha\lambda\|\Xi\|_{1}+\alpha(1-\lambda)\|\Xi\|_{2}^{2}\Bigg)\quad\text{subject to }\Xi\geq0.\nonumber
\end{align}
Here, $\|\cdot\|_{F}$ denotes the Frobenius norm, $\lambda\in[0,1]$
is a hyperparameter that interpolates linearly between LASSO~\cite{Tibshirani1996,Hastie2009}
and Ridge~\cite{Hoerl1} methods, and $\alpha\geq0$ is a hyperparameter
that, depending on $\lambda$, can induce sparsity and give preference
to smaller solutions in the $L_{1}$ or $L_{2}$ sense. For $\alpha=0$
the minimization problem reduces to standard least-squares (LSQ) with
the constraint $\Xi\geq0$. Reactive SINDy (\ref{method:minimizationproblem})
is therefore a generalization of the SINDy method to to the vector-valued
ansatz functions.

@@

We demonstrate the method by estimating the reactions of a gene-regulatory
network from time series of concentrations of the involved molecules.
Let $S:=\{A,B,C\}$ be a set of three species of proteins which are
being translated each from their respective $\mathrm{mRNA}$ molecule.
Each $\mathrm{mRNA}$ in turn has a corresponding $\mathrm{DNA}$
which it is transcribed from. The proteins and $\mathrm{mRNA}$ molecules
decay over time whereas the $\mathrm{DNA}$ concentration remains
constant. The network contains reactions of the following form~\cite{Thattai2001a}
\begin{align*}
\mathrm{DNA}_{i} & \rightharpoonup\mathrm{DNA}_{i}+\mathrm{mRNA}_{i} &  & \text{(transcription)},\\
\mathrm{mRNA}_{i} & \rightharpoonup\mathrm{mRNA}_{i}+i &  & \text{(translation)},\\
\mathrm{mRNA}_{i} & \rightharpoonup\emptyset &  & \text{(decay of mRNA)},\\
i & \rightharpoonup\emptyset &  & \text{(decay of protein)},\\
i+\mathrm{mRNA}_{j} & \rightharpoonup i &  & \text{(regulation of }j\in S\text{),}
\end{align*}
for each of the species $i\in S$. These reactions model a regulation
of species $j$ by virtue of the fact that the transcription product
inhibits the transcription processes. In our example proteins of type
$\mathrm{A}$ regulate the $\mathrm{mRNA}_{\mathrm{B}}$ molecules,
proteins of type $\mathrm{B}$ regulate the $\mathrm{mRNA}_{\mathrm{C}}$
molecules and proteins of type $\mathrm{C}$ regulate the $\mathrm{mRNA}_{\mathrm{A}}$
molecules (Fig.~\ref{fig:network}). Using this reaction model, time
series of concentrations are generated using the rates given in Tab~\ref{tab:reaction-library}
under the initial condition described in Tab~\ref{tab:Initial-conditions}a,
which were chosen so that all the reactions in the reaction model
significantly contribute to the temporal evolution of the system's
concentrations. The generation samples the integrated equations equidistantly
with a discrete time step of $\tau=3\cdot10^{-3}$ yielding $667$
frames which amounts to a cumulative time of roughly $T=2$.

\begin{figure}[h!]
\centering \includegraphics[width=\singlecolumnwidth]{figures_jcp/1.pdf}
\caption{\label{fig:network}The regulation network example described in Sec.~\ref{sec:results}.
Each circle depicts a species, each arrow corresponds to one reaction.
Blue arrows denote transcription from $\mathrm{DNA}$ to $\mathrm{mRNA}$,
green arrows denote translation from $\mathrm{mRNA}$ to protein,
and red arrows denote the regulatory network.}
\end{figure}
\begin{table}
\centering%
\ifthisispreprint
% ignore
\else
\resizebox{.95\columnwidth}{!}{%
\fi
\begin{tabular}{cccccccccc}
 & $\mathrm{DNA}_{\mathrm{A}}$ & $\mathrm{mRNA}_{\mathrm{A}}$ & $\mathrm{A}$ & $\mathrm{DNA}_{\mathrm{B}}$ & $\mathrm{mRNA}_{\mathrm{B}}$ & $\mathrm{B}$ & $\mathrm{DNA}_{\mathrm{C}}$ & $\mathrm{mRNA}_{\mathrm{C}}$ & $\mathrm{C}$\tabularnewline
\midrule
\textbf{(a)} & $1$ & $2$ & $0$ & $1$ & $0$ & $3$ & $1$ & $0$ & $0$\tabularnewline
\textbf{(b)} & $1$ & $1.5$ & $0$ & $1$ & $0$ & $2$ & $1$ & $0$ & $1$\tabularnewline
\end{tabular}
\ifthisispreprint
% ignore
\else
}
\fi
\caption{\label{tab:Initial-conditions}Initial conditions \textbf{(a)} and \textbf{(b)} used to generate
concentration time series. Reaction rates can be found in Tab.~\ref{tab:reaction-library}.}
\end{table}
The proposed estimation method is applied to analyze these time series
of concentrations in order to recover the underlying reaction network
from data. To this end we use the library of ansatz functions given
in Tab.~\ref{tab:reaction-library}, which contains a large number
of possible reactions, only few of which are actually part of the
model.

@@

We first set the hyperparameter $\alpha=0$ in the minimization problem
(\ref{method:minimizationproblem}), which results in constrained
least-squares regression without any of the regularization terms.
In this case we estimate a reaction network that can reproduce the
observations almost exactly (Fig.~\ref{fig:case-1-lsq}). However,
the result is mechanistically wrong as the sparsity pattern does not
match the reaction network used to generate the data. On the one hand
many spurious reactions are estimated that were not in the true reaction
scheme and would lead to wrong conclusions about the mechanism, such
as $\mathrm{A}+\mathrm{A}\rightharpoonup\mathrm{A}$ and $\mathrm{A}+\mathrm{C}\rightharpoonup\mathrm{C}$.
More dramatically, the reaction responsible for the decay of $\mathrm{A}$
particles is completely ignored (Fig.~\ref{fig:case-1-sparsity-pattern}).
\begin{figure}
\centering\includegraphics[width=\singlecolumnwidth]{figures_jcp/2.pdf}\caption{\label{fig:case-1-lsq}Concentration time series generated from integrating
the reaction network shown in Fig.~\ref{fig:network}a. The initial
condition prescribes positive concentration values only for $\mathrm{B}$
protein and $\mathrm{mRNA}_{\mathrm{A}}$ species (Tab.~\ref{tab:Initial-conditions}a).
This initial condition is used in the subsequent sections for further
analysis. Gray dots depict concentration time series yielded from
the LSQ rates estimated in Sec~\ref{sec:case-1}.}
\end{figure}

\ifthisispreprint
% ignore
\else
\onecolumngrid
\fi

\begin{figure}
\centering \includegraphics[width=0.82\doublecolumnwidth]{figures_jcp/3.pdf}
\caption{\label{fig:case-1-sparsity-pattern}Estimated reaction rates in the
system described in Sec.~\ref{sec:case-1}. The y and x axes contain
reaction educts and products, respectively. A circle at position $(i,j)$
represents a reaction $i\rightharpoonup j$ whose rate has a linear
relation with the area of the circle. The black outlines denote the
reactions with which the system was generated and contain the respective
rate value. Red crosses denote reactions that were used as additional
ansatz reactions. Blue circles are estimated by LSQ and orange circles
depict rates which were obtained by solving the minimization problem
(\ref{method:minimizationproblem}). The latter rates are subject
to a cutoff $\kappa=0.22$ corresponding to the green circle's area
under which a sparse solution with the correct processes can be recovered.
If a certain rate was estimated in both cases, two wedges instead
of one circle are displayed.}
\end{figure}
\ifthisispreprint
% ignore
\else
\twocolumngrid
\fi

Next, we sought sparse solutions by using $\alpha>0$ and additionally
eliminating reactions with rate constants smaller than a cutoff value
$\kappa$. For a suitable choice of hyperparameters $\alpha\approx1.91\cdot10^{-7}$,
$\lambda=1$, and $\kappa=0.22$, a sparse solution is obtained that
finds the correct reaction scheme and also recovers the decay reaction
(Fig.~\ref{fig:case-1-sparsity-pattern}).

@@

\begin{figure}
\centering \includegraphics[width=\singlecolumnwidth]{figures_jcp/4.pdf}
\caption{\label{fig:case2-convergence}Convergence of the estimation error
when estimating the system described in Sec.~\ref{sec:case-1} with
varying levels of noise by application of reactive SINDy (\ref{method:minimizationproblem})
with and without regularization in blue and orange, respectively.
The procedure was independently repeated $10$ times with different
realizations giving rise to the mean and standard deviation depicted
by solid lines and shaded areas, respectively. \textbf{(a)}: The number
of detected spurious reactions up to the cutoff value introduced in
Sec.~\ref{sec:case-1} over different levels of noise. \textbf{(b)}:
The estimation error given by the mean absolute error between the
generating reaction rates $\xi$ and the estimated reaction rates
$\hat{\xi}$ over different levels of noise.}
\end{figure}
The hyperparameters $(\alpha,\lambda)$ are obtained by shuffling
the data and performing a $10$-fold cross validation.

@@

\begin{figure}
\centering \includegraphics[width=\singlecolumnwidth]{figures_jcp/5.pdf}
\caption{\label{fig:case3-convergence}Convergence of estimation error of reaction
schemes from noisy gene-regulation data starting from two different
initial conditions under decreasing levels of noise. The minimization
problem (\ref{method:minimizationproblem}) was solved for $\alpha=0$
(LSQ) and with regularization. This was repeated $10$ times on different
sets of observation data generated by Gillespie SSA, giving rise to
mean and standard deviation (solid lines and shaded areas, respectively).
\textbf{(a)}: Concentration time series corresponding to the initial
conditions, generated by integrating the reaction-rate equations.
The first initial condition is identical to the one used in Sec.~\ref{sec:case-1}
and Sec.~\ref{sec:case-2}. The second initial condition (Tab.~\ref{tab:Initial-conditions}b)
prescribes positive initial concentrations for $\mathrm{mRNA}_{\mathrm{A}}$,
$\mathrm{B}$, and $\mathrm{C}$ species. The gray graphs are sample
realizations of integration using the Gillespie SSA. \textbf{(b)},\textbf{(c)}:
Analogously to Fig.~\ref{fig:case2-convergence} with the difference
that 20-fold cross validation was used for hyperparameter estimation.}
\end{figure}
The hyperparameters $(\alpha,\lambda)$ are obtained by shuffling
the data and performing a $20$-fold cross validation.

@@

\centering\includegraphics[width=\singlecolumnwidth]{figures_jcp/6.pdf}\caption{\label{fig:reaction-rates-sorted}Reaction rates sorted by their magnitude
to determine the cutoff $\kappa=0.22$ of Sec.~\ref{sec:case-1}.
The rates were estimated using the regularized minimization problem.}

@@

\ifthisispreprint
% ignore
\else
\onecolumngrid
\fi

@@

%\resizebox{.9\textwidth}{!}{%

@@

\end{tabular}\caption{\label{tab:reaction-library}Full set of ansatz reactions $\Theta$

@@

\ifthisispreprint
% ignore
\else
\twocolumngrid
\fi

\linespread{1.45}
